### 2022-09-29 main/frontmatter.tex
abstract tweaks

Nothing new appears, and supports the Standard Model in its continuing
successful extrapolation to the describe the most extreme behaviours colliding
protons.
Supersymmetry as a concept as not falsified by these results,
nor by the many similar observations.
But it is also not confirmed.

>>>>

Nothing new appears in the results.
This observation supports the Standard Model in its continuing successful
extrapolation to the describe the most extreme behaviours of proton collisions.
Supersymmetry as a concept as not falsified by this lack of visible new
phenomena, nor by the many similar observations.
But it is also not confirmed.
